Towards Practical First-Order Model Counting

### 2024-04-23 doc/paper.tex
The introductory part of Section 4

@@

\section{Smoothing (TODO)}

Goal of smoothing: whenever rules such as unit propagation or
inclusion-exclusion (maybe just these two?) eliminate the consideration of some
ground atoms, smoothing nodes should be inserted `at the same level' so that
these ground atoms are still considered when counting. Note that conjunction
nodes are irrelevant here because multiplication is associative. `At the same
level' means that, e.g., if some ground atoms were eliminated from consideration
before/after performing independent partial grounding, then the smoothing node
should also appear before/after the independent partial grounding node.

\todo[inline,caption={}]{
\begin{itemize}
  \item Cite something when introducing the idea of smoothing. Maybe both
        propositional and first-order sources.
  \item Can I prove that the additions to smoothing outlined in the rest of this
        section `do the right thing'?
\end{itemize}
}

@@

\subsection{Smoothing the FCG (TODO)}

\todo[inline,caption={}]{
  \begin{itemize}
    \item It seems like I'll need to introduce:
          \begin{itemize}
            \item FCGs
            \item node types (be consistent w.r.t.\ node vs vertex)
            \item their notation
          \end{itemize}
    \item Describe \cref{fig:smoothing1,fig:smoothing2}
    \item Introduce the compilation rules
  \end{itemize}
}

@@

Smoothing is a two-step process. First, atoms that are still accounted for in
the circuit are propagated upwards. Then, at vertices of certain types, missing
atoms are detected and additional sinks are created to account for them. If left
unchanged, the first step of this process would result in an infinite loop
whenever a cycle is encountered.

\subsection{Stage 1: Propagating Unit Clauses `Upwards' (TODO)}

@@

\subsection{Stage 2: Adding Smoothing Nodes (TODO)}

>>>>

\newcommand{\crefrangeconjunction}{--}

@@

\section{Smoothing}

Smoothness originates in propositional knowledge compilation where it is defined
as the property that, for every disjunction node, all disjuncts (as subtrees of
the circuit) contain the same atoms~\cite{darwiche2001tractable}. Van den Broeck
et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} generalise smoothness to
first-order logic, adding set-disjunction and inclusion-exclusion nodes
alongside disjunction.

The motivation for smoothing is as follows. Whenever compilation rules such as
unit propagation and inclusion-exclusion simplify the formula, some ground atoms
might be eliminated from consideration (see \cref{example:basecasesmoothing}
below). To account for them during counting, smoothing nodes (i.e., tautological
clauses such as $P(c) \lor \neg P(c)$) are added to the FCG at an appropriate
location.

In the rest of this section, we extend the smoothing algorithm of Van den Broeck
et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} even further.
\Cref{sec:smoothingbase} describes the role smoothing plays in the
base-case-finding algorithm from \cref{sec:main}. Then,
\cref{sec:smoothingfcg1,sec:smoothingfcg2,sec:smoothingfcg3} show how to adapt
smoothing to the compilation rules introduced by Dilkas and
Belle~\shortcite{DBLP:conf/kr/DilkasB23}.

@@

\subsection{Smoothing the FCG (TODO)}\label{sec:smoothingfcg1}

\todo[inline,caption={}]{
  \begin{itemize}
    \item introduce the relevant node types and their notation
    \item Describe \cref{fig:smoothing1,fig:smoothing2}
  \end{itemize}
}

@@

Smoothing is a two-step process. First, atoms that are still accounted for in
the circuit are propagated upwards. Then, at nodes of certain types, missing
atoms are detected and additional sinks are created to account for them. If left
unchanged, the first step of this process would result in an infinite loop
whenever a cycle is encountered.

\todo[inline]{Don't say `upwards'}

\subsection{Stage 1: Propagating Unit Clauses (TODO)}\label{sec:smoothingfcg2}

@@

\subsection{Stage 2: Adding Smoothing Nodes (TODO)}\label{sec:smoothingfcg3}
